---
title: "Katzen Einzelreports"
author: "Moritz Schneider"
date: "Monday, December 02, 2014"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[CO,CE]{Diffusionsreport Katzen}
output: pdf_document
---

#Auswertung Katzen

```{r, echo=FALSE}
datalist_directory <- "./data"
datalist_file <- "Data_list.csv"
source("./src/read_datalist.R")
source("./src/read_fitvalues.R")
source("./src/read_statistics.R")
source("./src/read_voxelvalues.R")
source("./src/get_median.R")
source("./src/get_delta.R")
source("./src/get_fits.R")
source("./src/get_paramindex.R")
datalist <- read_datalist(datalist_directory, datalist_file)
library("ggplot2")
library(knitr)
```

Available Data

```{r, echo=FALSE}
kable(datalist[,2:4])
voxelvalues <- read_voxelvalues(datalist)
cats <- summary(datalist$Name)
```

```{r, echo=FALSE}
median.table <- cbind(datalist[,1:3],
                  sapply(sapply(voxelvalues, function(x) x$ADC), median),
                  sapply(sapply(voxelvalues, function(x) x$Da), median),
                  sapply(sapply(voxelvalues, function(x) x$Db), median),
                  sapply(sapply(voxelvalues, function(x) x$f), median),
                  sapply(sapply(voxelvalues, function(x) x$Pf), median),
                  sapply(sapply(voxelvalues, function(x) x$Dk), median),
                  sapply(sapply(voxelvalues, function(x) x$K), median))
names(median.table) <- c("Katze.No", "Name", "Messung", "ADC[mm²/10³s]","D_slow[mm²/10³s]",
                         "D_fast[mm²/10³s]", "f[%]", "Pf[a.u.]",
                         "D_kurtosis[mm²/10³s]", "Kurtosis[a.u.]")
write.table(median.table, paste("./data/Median_values.csv"), sep=";", 
            row.names = FALSE)
```

\newpage

```{r, echo=FALSE, warning=FALSE}
cat = cats[1]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r overview, echo=FALSE, warning=FALSE}
dir.create(paste("./graphs/", names(cat), sep=""), showWarnings = FALSE)
medianADC <- array(cat*2-1)
medianDa <- array(cat*2-1)
medianDb <- array(cat*2-1)
medianf <- array(cat*2-1)
medianPf <- array(cat*2-1)
medianDk <- array(cat*2-1)
medianK <- array(cat*2-1)
messung <- array(cat*2-1)
for (i in 1:cat) {
        medianADC[i*2-1] <- median(as.numeric(voxelvalues[[paste(names(cat), i)]]$ADC))
        medianDa[i*2-1] <- median(as.numeric(voxelvalues[[paste(names(cat), i)]]$Da))
        medianDb[i*2-1] <- median(as.numeric(voxelvalues[[paste(names(cat), i)]]$Db))
        medianf[i*2-1] <- median(as.numeric(voxelvalues[[paste(names(cat), i)]]$f))
        medianPf[i*2-1] <- median(as.numeric(voxelvalues[[paste(names(cat), i)]]$Pf))
        medianDk[i*2-1] <- median(as.numeric(voxelvalues[[paste(names(cat), i)]]$Dk))
        medianK[i*2-1] <- median(as.numeric(voxelvalues[[paste(names(cat), i)]]$K))        
        messung[i*2-1] <- paste("Messung ", i)
        if (i > 1) {
                medianADC[i*2-2] <-  as.numeric(wilcox.test(
                        as.numeric(voxelvalues[[paste(names(cat), i)]]$ADC),
                        as.numeric(voxelvalues[[paste(names(cat), i-1)]]$ADC),
                        paired = FALSE)[3])
                medianDa[i*2-2] <- as.numeric(wilcox.test(
                        as.numeric(voxelvalues[[paste(names(cat), i)]]$Da),
                        as.numeric(voxelvalues[[paste(names(cat), i-1)]]$Da),
                        paired = FALSE)[3])
                medianDb[i*2-2] <- as.numeric(wilcox.test(
                        as.numeric(voxelvalues[[paste(names(cat), i)]]$Db),
                        as.numeric(voxelvalues[[paste(names(cat), i-1)]]$Db),
                        paired = FALSE)[3])
                medianf[i*2-2] <- as.numeric(wilcox.test(
                        as.numeric(voxelvalues[[paste(names(cat), i)]]$f),
                        as.numeric(voxelvalues[[paste(names(cat), i-1)]]$f),
                        paired = FALSE)[3])
                medianPf[i*2-2] <- as.numeric(wilcox.test(
                        as.numeric(voxelvalues[[paste(names(cat), i)]]$Pf),
                        as.numeric(voxelvalues[[paste(names(cat), i-1)]]$Pf),
                        paired = FALSE)[3])
                medianDk[i*2-2] <- as.numeric(wilcox.test(
                        as.numeric(voxelvalues[[paste(names(cat), i)]]$Dk),
                        as.numeric(voxelvalues[[paste(names(cat), i-1)]]$Dk),
                        paired = FALSE)[3])
                medianK[i*2-2] <- as.numeric(wilcox.test(
                        as.numeric(voxelvalues[[paste(names(cat), i)]]$K),
                        as.numeric(voxelvalues[[paste(names(cat), i-1)]]$K),
                        paired = FALSE)[3])
                messung[i*2-2] <- "p-wert"
        }
}
digits <- 5 
MedianValues <- data.frame(messung, signif(medianADC, digits),
                           signif(medianDa, digits), signif(medianDb, digits), 
                           signif(medianf, digits), signif(medianPf, digits), 
                           signif(medianDk, digits), signif(medianK, digits))
names(MedianValues) <- c("Messung", "ADC", "D_slow", "D_fast", "Perf f", "Pseudoflow", "D_k", "Kurtosis")
kable(MedianValues)
```

##ADC

```{r ADChist, echo=FALSE, warning=FALSE}
par(mfrow = c(cat,1), mar = c(4,4,2,1))
for (i in 1:cat) {
        hist(as.numeric(voxelvalues[[paste(names(cat), i)]]$ADC), 
             col = i+6, xlim = c (0.5,3.5), 
             breaks = seq(0,100,by=0.05),  
             main = paste("ADC Histogram Messung", i, ", Median", medianADC[i*2-1]), 
             xlab = paste("ADC [mm²/10³s]"), 
             ylab = paste("Count"))
        rug(as.numeric(voxelvalues[[paste(names(cat), i)]]$ADC))
        abline( v = median(as.numeric(voxelvalues[[paste(names(cat), i)]]$ADC)), col = "magenta", lwd =4)
}
invisible(dev.print(pdf, paste("./graphs/", names(cat), "/", names(cat), "ADChist.pdf", sep="")))
invisible(dev.off())
```


```{r ADCgg, echo=FALSE, warning=FALSE}
tempnames <- c(1:cat)
templist <- sapply(tempnames,function(x) NULL)
for (i in 1:cat) {        
        templist[[i]] <- data.frame(as.numeric(voxelvalues[[paste(names(cat), i)]]$ADC))
        templist[[i]]$messung <- as.character(i)
        names(templist[[i]]) <- paste(c("plotdata", "Messung"))        
}
plotdata <- templist[[1]]
for (i in 2:cat) {
        plotdata <- rbind(plotdata, templist[[i]])
}
ggplot(plotdata, aes(plotdata, fill = Messung)) + 
        xlab("ADC [mm²/10³s]") + 
        ggtitle("ADC Histogramme") + 
        geom_density(alpha = 0.4, adjust = 1) + 
        xlim(0.5, 3.5)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "ADCgg.pdf", sep=""),
       width = 6.5, height = 4.5)
ggplot(plotdata, aes(plotdata, fill = Messung)) + 
        xlab("ADC [mm²/10³s]") + ggtitle("ADC Histogramme") + 
        geom_histogram(alpha = 0.4, aes(y = ..density..), position = 'identity', binwidth = 0.05) + 
        xlim(0.5, 3.5)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "ADCgg2.pdf", sep=""),
       width = 6.5, height = 4.5)
```

##D_slow

```{r Dahist, echo=FALSE, warning=FALSE}
par(mfrow = c(cat,1), mar = c(4,4,2,1))
for (i in 1:cat) {
        hist(as.numeric(voxelvalues[[paste(names(cat), i)]]$Da), 
             col = i+6, xlim = c (0.5,3.5), breaks = seq(0,100,by=0.05),  
             main = paste("Da Histogram Messung", i, ", Median", medianDa[i*2-1]), 
             xlab = paste("Da [mm²/10³s]"), 
             ylab = paste("Count"))
        rug(as.numeric(voxelvalues[[paste(names(cat), i)]]$Da))
        abline( v = median(as.numeric(voxelvalues[[paste(names(cat), i)]]$Da)), col = "magenta", lwd =4)
}
invisible(dev.print(pdf, paste("./graphs/", names(cat), "/", names(cat), "DAhist.pdf", sep="")))
invisible(dev.off())
```


```{r Dagg, echo=FALSE, warning=FALSE}
tempnames <- c(1:cat)
templist <- sapply(tempnames,function(x) NULL)
for (i in 1:cat) {
        templist[[i]] <- data.frame(as.numeric(voxelvalues[[paste(names(cat), i)]]$Da))
        templist[[i]]$messung <- as.character(i)
        names(templist[[i]]) <- paste(c("plotdata", "Messung"))
}
plotdata <- templist[[1]]
for (i in 2:cat) {
        plotdata <- rbind(plotdata, templist[[i]])
}
ggplot(plotdata, aes(plotdata, fill = Messung)) + xlab("Da [mm²/10³s]") +
        ggtitle("Da Histogramme") +
        geom_density(alpha = 0.4, adjust = 1) + xlim(0.5, 3.5)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Dagg.pdf", sep=""),
       width = 6.5, height = 4.5)
ggplot(plotdata, aes(plotdata, fill = Messung)) +
        xlab("Da [mm²/10³s]") + ggtitle("Da Histogramme") +
        geom_histogram(alpha = 0.4, aes(y = ..density..), position = 'identity', binwidth = 0.05)+ 
        xlim(0.5, 3.5)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Dagg2.pdf", sep=""),
       width = 6.5, height = 4.5)
```

##D_fast

```{r Dbhist, echo=FALSE, warning=FALSE}
par(mfrow = c(cat,1), mar = c(4,4,2,1))
for (i in 1:cat) {
        hist(as.numeric(voxelvalues[[paste(names(cat), i)]]$Db), 
             col = i+6, xlim = c (1,15), breaks = seq(0,100,by=0.2),  
             main = paste("Db Histogram Messung", i, ", Median", medianDb[i*2-1]), 
             xlab = paste("Db [mm²/10³s]"), ylab = paste("Count"))
        rug(as.numeric(voxelvalues[[paste(names(cat), i)]]$Db))
        abline( v = median(as.numeric(voxelvalues[[paste(names(cat), i)]]$Db)), col = "magenta", lwd =4)
}
invisible(dev.print(pdf, paste("./graphs/", names(cat), "/", names(cat), "Dbhist.pdf", sep="")))
invisible(dev.off())
```


```{r Dbgg, echo=FALSE, warning=FALSE}
tempnames <- c(1:cat)
templist <- sapply(tempnames,function(x) NULL)
for (i in 1:cat) {
        templist[[i]] <- data.frame(as.numeric(voxelvalues[[paste(names(cat), i)]]$Db))
        templist[[i]]$messung <- as.character(i)
        names(templist[[i]]) <- paste(c("plotdata", "Messung"))
}
plotdata <- templist[[1]]
for (i in 2:cat) {
        plotdata <- rbind(plotdata, templist[[i]])
}
ggplot(plotdata, aes(plotdata, fill = Messung)) + xlab("Db [mm²/10³s]") +
        ggtitle("Db Histogramme") +
        geom_density(alpha = 0.4, adjust = 1) + xlim(1, 15)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Dbgg.pdf", sep=""),
       width = 6.5, height = 4.5)
ggplot(plotdata, aes(plotdata, fill = Messung)) +
        xlab("Db [mm²/10³s]") + ggtitle("Db Histogramme") +
        geom_histogram(alpha = 0.4, aes(y = ..density..), position = 'identity', binwidth = 0.2) + 
        xlim(1, 15)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Dbgg2.pdf", sep=""),
       width = 6.5, height = 4.5)
```

##Perfusion f

```{r fhist, echo=FALSE, warning=FALSE}
par(mfrow = c(cat,1), mar = c(4,4,2,1))
for (i in 1:cat) {
        hist(as.numeric(voxelvalues[[paste(names(cat), i)]]$f), 
             col = i+6, xlim = c (0,30), breaks = seq(0,100,by=0.5),  
             main = paste("f Histogram Messung", i, ", Median", medianf[i*2-1]), 
             xlab = paste("f [%]"), ylab = paste("Count"))
        rug(as.numeric(voxelvalues[[paste(names(cat), i)]]$f))
        abline( v = median(as.numeric(voxelvalues[[paste(names(cat), i)]]$f)), col = "magenta", lwd =4)
}
invisible(dev.print(pdf, paste("./graphs/", names(cat), "/", names(cat), "fhist.pdf", sep="")))
invisible(dev.off())
```


```{r fgg, echo=FALSE, warning=FALSE}
tempnames <- c(1:cat)
templist <- sapply(tempnames,function(x) NULL)
for (i in 1:cat) {
        templist[[i]] <- data.frame(as.numeric(voxelvalues[[paste(names(cat), i)]]$f))
        templist[[i]]$messung <- as.character(i)
        names(templist[[i]]) <- paste(c("plotdata", "Messung"))
}
plotdata <- templist[[1]]
for (i in 2:cat) {
        plotdata <- rbind(plotdata, templist[[i]])
}
ggplot(plotdata, aes(plotdata, fill = Messung)) + xlab("f [%]") +
        ggtitle("f Histogramme") +
        geom_density(alpha = 0.4, adjust = 1) + xlim(0, 30)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "fgg.pdf", sep=""),
       width = 6.5, height = 4.5)
ggplot(plotdata, aes(plotdata, fill = Messung)) +
        xlab("f [%]") + ggtitle("f Histogramme") +
        geom_histogram(alpha = 0.4, aes(y = ..density..), position = 'identity', binwidth = 0.5) + 
        xlim(0, 30)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "fgg2.pdf", sep=""),
       width = 6.5, height = 4.5)
```

##Pseudoflow D_fast*f

```{r Pfhist, echo=FALSE, warning=FALSE}
par(mfrow = c(cat,1), mar = c(4,4,2,1))
for (i in 1:cat) {
        hist(as.numeric(voxelvalues[[paste(names(cat), i)]]$Pf), 
             col = i+6, xlim = c (0,500), breaks = seq(0,5000,by=5),  
             main = paste("Pf Histogram Messung", i, ", Median", medianPf[i*2-1]), 
             xlab = paste("Pf [mm²/10³s*%]"), ylab = paste("Count"))
        rug(as.numeric(voxelvalues[[paste(names(cat), i)]]$Pf))
        abline( v = median(as.numeric(voxelvalues[[paste(names(cat), i)]]$Pf)), col = "magenta", lwd =4)
}
invisible(dev.print(pdf, paste("./graphs/", names(cat), "/", names(cat), "Pfhist.pdf", sep="")))
invisible(dev.off())
```


```{r Pfgg, echo=FALSE, warning=FALSE}
tempnames <- c(1:cat)
templist <- sapply(tempnames,function(x) NULL)
for (i in 1:cat) {
        templist[[i]] <- data.frame(as.numeric(voxelvalues[[paste(names(cat), i)]]$Pf))
        templist[[i]]$messung <- as.character(i)
        names(templist[[i]]) <- paste(c("plotdata", "Messung"))
}
plotdata <- templist[[1]]
for (i in 2:cat) {
        plotdata <- rbind(plotdata, templist[[i]])
}
ggplot(plotdata, aes(plotdata, fill = Messung)) + xlab("Pf [mm²/10³s*%]") +
        ggtitle("Pf Histogramme") +
        geom_density(alpha = 0.4, adjust = 1) + xlim(0, 500)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Pfgg.pdf", sep=""),
       width = 6.5, height = 4.5)
ggplot(plotdata, aes(plotdata, fill = Messung)) +
        xlab("Pf [mm²/10³s*%]") + ggtitle("Pf Histogramme") +
        geom_histogram(alpha = 0.4, aes(y = ..density..), position = 'identity', binwidth = 5) + 
        xlim(0, 500)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Pfgg2.pdf", sep=""),
       width = 6.5, height = 4.5)
```

##D Kurtosis

```{r Dkhist, echo=FALSE, warning=FALSE}
par(mfrow = c(cat,1), mar = c(4,4,2,1))
for (i in 1:cat) {
        hist(as.numeric(voxelvalues[[paste(names(cat), i)]]$Dk), 
             col = i+6, xlim = c (0.5,3.5), breaks = seq(0,100,by=0.05),  
             main = paste("Dk Histogram Messung", i, ", Median", medianDk[i*2-1]), 
             xlab = paste("Dk [mm²/10³s]"), ylab = paste("Count"))
        rug(as.numeric(voxelvalues[[paste(names(cat), i)]]$Dk))
        abline( v = median(as.numeric(voxelvalues[[paste(names(cat), i)]]$Dk)), col = "magenta", lwd =4)
}
invisible(dev.print(pdf, paste("./graphs/", names(cat), "/", names(cat), "Dkhist.pdf", sep="")))
invisible(dev.off())
```


```{r Dkgg, echo=FALSE, warning=FALSE}
tempnames <- c(1:cat)
templist <- sapply(tempnames,function(x) NULL)
for (i in 1:cat) {
        templist[[i]] <- data.frame(as.numeric(voxelvalues[[paste(names(cat), i)]]$Dk))
        templist[[i]]$messung <- as.character(i)
        names(templist[[i]]) <- paste(c("plotdata", "Messung"))
}
plotdata <- templist[[1]]
for (i in 2:cat) {
        plotdata <- rbind(plotdata, templist[[i]])
}
ggplot(plotdata, aes(plotdata, fill = Messung)) + xlab("Dk [mm²/10³s]") +
        ggtitle("Dk Histogramme") +
        geom_density(alpha = 0.4, adjust = 1) + xlim(0.5, 3.5)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Dkgg.pdf", sep=""),
       width = 6.5, height = 4.5)
ggplot(plotdata, aes(plotdata, fill = Messung)) +
        xlab("Dk [mm²/10³s]") + ggtitle("Dk Histogramme") +
        geom_histogram(alpha = 0.4, aes(y = ..density..), position = 'identity', binwidth = 0.05) + 
        xlim(0.5, 3.5)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Dkgg2.pdf", sep=""),
       width = 6.5, height = 4.5)
```

##Kurtosis

```{r Khist, echo=FALSE, warning=FALSE}
par(mfrow = c(cat,1), mar = c(4,4,2,1))
for (i in 1:cat) {
        plotdata = as.numeric(voxelvalues[[paste(names(cat), i)]]$K)
        plotdata[plotdata <= -100] = -100
        hist(plotdata, 
             col = i+6, 
             xlim = c (-1,2), 
             breaks = seq(-101,100,by=0.05),  
             main = paste("K Histogram Messung", i, ", Median", medianK[i*2-1]), 
             xlab = paste("K [a.u.]"), 
             ylab = paste("Count"))
        rug(as.numeric(voxelvalues[[paste(names(cat), i)]]$K))
        abline( v = median(as.numeric(voxelvalues[[paste(names(cat), i)]]$K)), col = "magenta", lwd =4)
}
invisible(dev.print(pdf, paste("./graphs/", names(cat), "/", names(cat), "Khist.pdf", sep="")))
invisible(dev.off())
```


```{r Kgg, echo=FALSE, warning=FALSE}
tempnames <- c(1:cat)
templist <- sapply(tempnames,function(x) NULL)
for (i in 1:cat) {
        templist[[i]] <- data.frame(as.numeric(voxelvalues[[paste(names(cat), i)]]$K))
        templist[[i]]$messung <- as.character(i)
        names(templist[[i]]) <- paste(c("plotdata", "Messung"))
}
plotdata <- templist[[1]]
for (i in 2:cat) {
        plotdata <- rbind(plotdata, templist[[i]])
}
ggplot(plotdata, aes(plotdata, fill = Messung)) + xlab("K [a.u.]") +
        ggtitle("K Histogramme") +
        geom_density(alpha = 0.4, adjust = 1) + xlim(-1, 2)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Kgg.pdf", sep=""),
       width = 6.5, height = 4.5)
ggplot(plotdata, aes(plotdata, fill = Messung)) +
        xlab("K [a.u.]") + ggtitle("K Histogramme") +
        geom_histogram(alpha = 0.4, aes(y = ..density..), position = 'identity', binwidth = 0.05) + 
        xlim(-1, 1)
ggsave(paste("./graphs/", names(cat), "/", names(cat), "Kgg2.pdf", sep=""),
       width = 6.5, height = 4.5)
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[2]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat2overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat2ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat2ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat2Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat2Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat2Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat2Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat2fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat2fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat2Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat2Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat2Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat2Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat2Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat2Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[3]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat3overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat3ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat3ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat3Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat3Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat3Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat3Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat3fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat3fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat3Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat3Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat3Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat3Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat3Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat3Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[4]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat4overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat4ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat4ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat4Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat4Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat4Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat4Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat4fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat4fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat4Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat4Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat4Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat4Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat4Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat4Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[5]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat5overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat5ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat5ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat5Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat5Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat5Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat5Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat5fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat5fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat5Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat5Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat5Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat5Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat5Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat5Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[6]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat6overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat6ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat6ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat6Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat6Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat6Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat6Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat6fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat6fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat6Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat6Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat6Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat6Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat6Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat6Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[7]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat7overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat7ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat7ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat7Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat7Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat7Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat7Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat7fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat7fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat7Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat7Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat7Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat7Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat7Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```



```{r cat7Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```
```{r, echo=FALSE, warning=FALSE}
cat = cats[8]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat8overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat8ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat8ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat8Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat8Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat8Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat8Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat8fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat8fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat8Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat8Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat8Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat8Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat8Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat8Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[9]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat9overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat9ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat9ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat9Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat9Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat9Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat9Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat9fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat9fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat9Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat9Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat9Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat9Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat9Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat9Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[10]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat10overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat10ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat10ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat10Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat10Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat10Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat10Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat10fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat10fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat10Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat10Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat10Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat10Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat10Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat10Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[11]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat11overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat11ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat11ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat11Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat11Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat11Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat11Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat11fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat11fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat11Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat11Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat11Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat11Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat11Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat11Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```



```{r, echo=FALSE, warning=FALSE}
cat = cats[12]
```

#Report `r names(cat)`

##Übersicht Median-Werte

```{r cat12overview, ref.label='overview', echo=FALSE, warning=FALSE}
```

##ADC

```{r cat12ADChist, ref.label='ADChist', echo=FALSE, warning=FALSE}
```


```{r cat12ADCgg, ref.label='ADCgg', echo=FALSE, warning=FALSE}
```

##D_slow

```{r cat12Dahist, ref.label='Dahist', echo=FALSE, warning=FALSE}
```


```{r cat12Dagg, ref.label='Dagg', echo=FALSE, warning=FALSE}
```

##D_fast

```{r cat12Dbhist, ref.label='Dbhist', echo=FALSE, warning=FALSE}
```


```{r cat12Dbgg, ref.label='Dbgg', echo=FALSE, warning=FALSE}
```

##Perfusion f

```{r cat12fhist, ref.label='fhist', echo=FALSE, warning=FALSE}
```


```{r cat12fgg, ref.label='fgg', echo=FALSE, warning=FALSE}
```

##Pseudoflow D_fast*f

```{r cat12Pfhist, ref.label='Pfhist', echo=FALSE, warning=FALSE}
```


```{r cat12Pfgg, ref.label='Pfgg', echo=FALSE, warning=FALSE}
```

##D Kurtosis

```{r cat12Dkhist, ref.label='Dkhist', echo=FALSE, warning=FALSE}
```


```{r cat12Dkgg, ref.label='Dkgg', echo=FALSE, warning=FALSE}
```

##Kurtosis

```{r cat12Khist, ref.label='Khist', echo=FALSE, warning=FALSE}
```


```{r cat12Kgg, ref.label='Kgg', echo=FALSE, warning=FALSE}
```